Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-23 article.tex
bookmark

Lightfield and integral imaging~\cite{bishop,horstmeyer,kim,Ng1948}
samples the optical radiance distribution in location and
direction. It is mainly used in small-scale setups. This paper deals
with a huge scale, up to Earth's size.  The atmosphere allows light to
pass through in multiple locations and directions. Light is affected
by this medium. Therefore, in this paper we lay out a principle to
recover this 3D medium using measured and modeled lightfields
(Fig.~\ref{fig:groundgrid}).
\begin{figure*}[t!]
  \begin{center}
    \includegraphics[width=\linewidth]{images/groundtomog24.pdf}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras. Our tomographic
    reconstruction follows the acquisition. The atmosphere is analyzed
    in a voxel grid.}
  \label{fig:groundgrid}
\end{figure*}
Projecting this large object to various directions is similar to
tomography in other scientific domains. However, the formulation here
is distinct. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{gorbunov,messer}. In contrast,
our source is the uncontrolled, unidirectional Sun. Moreover, typical
tomography relies on a linear model~\cite{gregson}: the pixel value is
a linear combination of components along a line of sight (LOS), or a
multiplicative combination (linearized by a logarithm). Linear
tomography can detect volcanic gas~\cite{wright}, which absorbs
UV. Other gases in the atmosphere absorb IR. However, in visible
light, atmospheric attenuation is typically dominated by {\em
  scattering} by particles (aerosols), rather than absorption by
gasses. Thus, in our problem, we cannot rely on direct illumination,
but on sunlight scattered into the LOS.  The model turns out to be
{\em nonlinear, yet tractable}.

@@

The atmosphere has a non-uniform distribution of scattering
aerosols. We seek to recover this 3D volumetric distribution. To solve
this problem, we formulate a process analogous to tomographic
reconstruction. The scene is projected to multiple directions. Thus, a
system captures integrated radiance as a function of direction and 2D
projected location. Any voxel in the atmosphere contributes to the
integrated radiance in multiple directional measurements
(Fig.~\ref{fig:groundgrid}). The measurements then provide a large
number of constraints, to recover the distribution: the density and
type of aerosols, per voxel.
Earth's radiation is sampled both spatially and angularly from
space~\cite{breon,diner,Martonchikc,vanMol}. However, current
multiview spaceborne systems are very coarse. For example, aerosol
retrieval in the most complex instrument, MISR, requires spatial
blocks that are about $17\times 17$km wide, each observed from just 9
views along-track. This practically leads to vertical radiative
transfer analysis, degenerating atmospheric analysis to
1D. Experimental airborne instruments under
development~\cite{baxter,dinerDavis10} may provide better, if still
coarse resolution once they are operational.

We believe that high resolution atmospheric recovery can be achieved
by a large set of ground-based wide-angle~\cite{Cossairt2011,
  Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
sky-cameras, looking upwards and capturing the sky lightfield.
Moreover, satellites image close to the orbit track (a 1D array of
viewpoints). In contrast, land-based cameras can form a 2D set of
viewpoints~\cite{DBLP:journals/pieee/SnavelySGSS10} as easy or hard as
a 1D grid~\cite{Joshi06naturalvideo}. However, before designing and
setting up such a very large scale system requires assessment of many
details that had not been explored. These include camera
specifications needed to recover typical distributions. Hence, a major
theoretic and numerical research phase is ahead.

This paper takes the first step, of formulating this principle and
demonstrating feasibility using realistic simulations. The formulation
of this paper can also apply to multiview images that are captured
from satellites, for future spaceborne instruments of this capacity.

@@

\subfile{monte_carlo}

@@

@@

\noindent{\bf Dimensions}: The domain of sky we simulate and recover
has area of \SI{50 x 50}{\km}, and it extends from the ground up to
altitude of \SI{10}{\km}. This volume is divided to a \num{50 x 50 x
  100} grid, where each voxel has area of \SI{1 x 1}{\km} and vertical
thickness of \SI{100}{\metre}. The dimension of the problem is thus
$250,000$ variables.

@@

We simulated various spatial distributions. All were set as a product
of two functions. The first function is an exponential
decay~\cite{Levi1980} with altitude $h(k)$ of voxel $k$,
\begin{align}
  w_1[h(k)] = \frac{1} {\sigma^{\rm aerosol}_{\rm G} \mathrm{MFP^{sea
        level}}} \exp\left[-\frac{h(k)}{H^\mathrm{aerosol}}\right],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. This expresses a general trend
of reduced atmospheric density with height. Here the mean free path
(MFP) of the aerosols layer at sea level was set to \linebreak
\mbox{$\mathrm{MFP^{sea level}}=1/5$~\si{\per\km}}.

\todo[inline]{Update the quantities above especially the visibility or
  fix the images}

The second function, $w_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  w_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bm n}^{\rm true}={\bm w}_1\odot {\bm w}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:simulation1}a):
\begin{figure} \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation1}}
  \caption{\small [a] Simulated 3D aerosol distribution composed of
    {\em Haze Blobs}. [b] Its reconstruction. Color represents aerosol
    density. The density units are $10^{15}~{\rm particles}/{\rm
      cm}^3.$}
  \label{fig:simulation1}
\end{figure}
the first is centered at altitude \SI{3.3}{\km}, and has horizontal
width of \SI{32}{\km} and vertical thickness of \SI{2.8}{\km}. The
second ellipsoid is centered at altitude \SI{6.6}{\km}, and has
lateral width of \SI{24}{\km} and vertical thickness of
\SI{2.1}{\km}. Note that the horizontal widths are much larger than
the vertical ones. This is consistent with scales of atmospheric
aerosol distributions.

\noindent{\bf Cameras}: Each ground-based camera has a hemispherical
field of view, capturing the entire sky from its viewpoint. We used
100 viewpoints on a grid, each view \SI{\approx 4.4}{\km} from its
neighbors.  The resolution of each camera is low: \num{128 x 128}
pixels, expressing the fact that cloudless (yet hazy) sky images are
rather smooth, hence there is no need for high image resolution. Each
pixel has full-well depth of 40000 electrons, which corresponds to the
brightest pixel value. Each measurement has photon noise, which is
Poissonian distributed, according to each image-pixel value $i_c$ and
the full-well depth. For example, \cref{fig:simulation-results1}a
shows an example of a modeled photograph
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.7\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MCRT simulation (\cref{sec:monte-carlo-simul}).}
  \label{fig:simulation-results1}
\end{figure}
of the {\em Haze Blobs} scene that corresponds to
\cref{fig:simulation1}a.

\noindent{\bf Computer}: We had access to an SGI-TNN cluster computer
that has 88 computer nodes consisting of two 2.40 GHz six-Core Xeon
with 8GB DDR3 memory per core. Out of it, we used 8 nodes,
corresponding to 96 cores. Each core was dedicated to rendering a
modeled image (in each interaction) as if captured by one of the 95
cameras. Each iteration (varying the model according to the
gradient-based algorithm and varying all the rendered images) took
\SI{\approx 7}{\second}.

>>>>

Lightfield and integral imaging~\cite{bishop,horstmeyer,kim,Ng1948}
samples the optical radiance distribution in location and
direction. It is mainly used in small-scale setups. This paper deals
with a huge scale, up to Earth's size.  The atmosphere allows light to
pass through in multiple locations and directions. Light is affected
by this medium. Therefore, in this paper we lay out a principle to
recover this 3D medium using measured and modeled lightfields
(Fig.~\ref{fig:groundgrid}).
\begin{figure*}[t!]
  \begin{center}
    \includegraphics[width=\linewidth]{images/groundtomog24.pdf}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras.}
  \label{fig:groundgrid}
\end{figure*}
Projecting this large object to various directions is similar to
tomography in other scientific domains. However, the formulation here
is distinct. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{gorbunov,messer}. In contrast,
our source is the uncontrolled, unidirectional Sun. Moreover, typical
tomography relies on a linear model~\cite{gregson}: the pixel value is
a linear combination of components along a line of sight (LOS), or a
multiplicative combination (linearized by a logarithm). Linear
tomography can detect volcanic gas~\cite{wright}, which absorbs
UV. Other gases in the atmosphere absorb IR. However, in visible
light, atmospheric attenuation is typically dominated by {\em
  scattering} by particles (aerosols), rather than absorption by
gasses. Thus, in our problem, we cannot rely on direct illumination,
but on sunlight scattered into the LOS.  The model turns out to be
{\em nonlinear, yet tractable}.

@@

We believe that high resolution atmospheric recovery can be achieved
by a large set of ground-based wide-angle~\cite{Cossairt2011,
  Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
sky-cameras, looking upwards and capturing the sky lightfield.  This
paper takes the first step, of formulating this principle and
demonstrating feasibility using realistic simulations. The formulation
of this paper can also apply to multiview images that are captured
from satellites, for future spaceborne instruments of this capacity.

We simulate image acquisition using Monte Carlo simulations
(\cref{sec:monte-carlo-simul}).  Monte carlo model multiple scattering
and therefore enable simulating realistic scenarios. Our
reconstruction algorithm is based on the Single-Scattering model
(\cref{sec:single-scatt-model}). The Single-Scattering approximation
enables state the solution to the Radiative Transform in a closed
form. This closed is beneficial to us as it enables us to invert the
model and thus recover the underlying atmosphere
(\cref{sec:inverse-problem}).

@@

@@

\section{Monte Carlo RT}
\label{sec:monte-carlo-simul}

Monte Carlo (MC) methods enable rigorous modeling of photon
propagation in the atmosphere. The radiative transfer is expressed as
probability distributions which describe the distance travelled by the
photon between scatterings and the angle of deflection at each
scatter.  This enables simulating multiple scattering and produce
realistic results.  MC simulations can be made arbitrarily accurate by
increasing the number of photons.  Another advantage of the MC methods
is that they are highly parallelable.

The MC simulations use the same atmosphere grid described in
\cref{sec:single-scatt-model}. we use backward MC, i.e. photons are
traced from the detector to the sun. Photons are emitted from each
pixel of the camera in the direction determined by the camera
model. The optical distance that the photon travels before scattering
is determined according to the Beer-Lambert law~\cref{eq:beer-lambert}
and the inversion sampling method. Once the optical distance is
determined the ``real'' distance is determined by summing the optical
depth of the discrete voxels (\cref{sec:optical-depth}) along the
photon direction till the desired optical distance is reached.  At
each scattering event, first the type of aerosol is determined by
sampling the different aerosols distributions inside the voxel. The
new direction is determined by inverse sampling the phase function of
the relevant aerosols: Rayleigh, \cref{eq:rayleighP} or
Henyey-Greenstein \cref{eq:aerosol_scatter}.  To accelerate the MC we
use the local estimation (LE) method.

@@

\noindent{\bf Dimensions}: The domain of sky we simulate and recover
has area of \SI{50 x 50}{\km}, and it extends from the ground up to
altitude of \SI{10}{\km}. This volume is divided into a rectilinear
grid. We used different grid sizes from \num{50 x 50 x 100} grid,
where each voxel has area of \SI{1 x 1}{\km} and vertical thickness of
\SI{100}{\metre} and down to num{10 x 10 x 20} grid, where each voxel
has area of \SI{5 x 5}{\km} and vertical thickness of
\SI{500}{\metre}. The different grid sizes determine the number of
variables.

@@

We simulated various spatial distributions. All were set as a product
of two functions. The first function is an exponential
decay~\cite{Levi1980} with altitude $h(k)$ of voxel $k$,
\begin{align}
  w_1[h(k)] = \frac{1} {n^{sea level}}
  \exp\left[-\frac{h(k)}{H^\mathrm{aerosol}}\right],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. This expresses a general trend
of reduced atmospheric density with height.

The second function, $w_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  w_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bm n}^{\rm true}={\bm w}_1\odot {\bm w}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:simulation1}a):
\begin{figure} \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/simulation1}}
  \caption{\small [a] Simulated 3D aerosol distribution composed of
    {\em Haze Blobs} and [b] its reconstruction. Color represents
    aerosol density. The density units are $10^{15}~{\rm
      particles}/{\rm cm}^3.$}
  \label{fig:simulation1}
\end{figure}
the first is centered at altitude \SI{3.3}{\km}, and has horizontal
width of \SI{32}{\km} and vertical thickness of \SI{2.8}{\km}. The
second ellipsoid is centered at altitude \SI{6.6}{\km}, and has
lateral width of \SI{24}{\km} and vertical thickness of
\SI{2.1}{\km}. Note that the horizontal widths are much larger than
the vertical ones. This is consistent with scales of atmospheric
aerosol distributions.

\noindent{\bf Cameras}: The cameras are created by the MC simulations.
Each ground-based camera has a hemispherical field of view, capturing
the entire sky from its viewpoint. Again, we used different numbers of
cameras ranging from 100 viewpoints to 12. The cameras are arranged on
a grid.  The resolution of each camera is low, expressing the fact
that cloudless (yet hazy) sky images are rather smooth, hence there is
no need for high image resolution.  For example,
\cref{fig:simulation-results1}b shows an example of a modeled
photograph
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.7\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MCRT simulation (\cref{sec:monte-carlo-simul}).}
  \label{fig:simulation-results1}
\end{figure}
of the {\em Haze Blobs} scene that corresponds to
\cref{fig:simulation1}a.

\noindent{\bf Computer}: We had access to an SGI-TNN cluster computer
that has 88 computer nodes consisting of two 2.40 GHz six-Core Xeon
with 8GB DDR3 memory per core. The number of cures used is depends
on the size of the simulations. Each core was dedicated to rendering a
modeled image.
